Methods with preconditioning with weight decay regularization

### 2023-04-12 paper/main.tex
add review on Nikita's article

@@

\begin{theorem}
    Suppose the Assumption 1, 2, 4, 5 and let $\varepsilon > 0$ and let the step-size satisfy
    \begin{equation*}
        \eta \leq \frac{2 \alpha}{\tilde{L}}
    \end{equation*}
    Then, the number of iterations performed by AdamW algorithm, starting from an initial point $w_0 \in \mathbb{R}^d$ with $\Delta_0 = \tilde{F}(w_0) - \tilde{F}^*$, required to obtain and $\varepsilon$-approximate solution of the convex problem (link here to problem 1) can be bounded by
    \begin{equation*}
        T =  \mathcal{O}\left( \frac{\ln \frac{\Delta_0}{\epsilon}}{2 \mu \eta^2(\frac{1}{\eta} - \frac{\tilde{L}}{2 \alpha})} \right)
    \end{equation*}
\end{theorem}
\section{Appendix}

@@

\bibliographystyle{unsrtnat}
\bibliography{references}

>>>>

The OASIS algorithm differs from Adam in that it updates the learning rate and calculates the pseudo-Hessian matrix at each step using the expectation and a random variable distributed according to the Rademacher distribution.

This is OASIS, the main difference from Adam is how the Hessian is considered, but when proving convergence, this will not play any role.
\begin{algorithm}[H]
\caption{OASIS}\label{alg:OASIS}
\begin{algorithmic}
    \Require{$w_0, \eta_0, D_0, \theta_0 = + \infty$}    
    \State $w_1 = w_0 - \eta \hat{D_0}^{-1} \nabla F(w_0)$

    \For{$k = 1, 2, ...$}
    \State $D_k = \beta D_{k-1} + (1-\beta_2) \cdot diag\left( z_k \odot \nabla^2 F(w_k) z_k \right)$
    \State $(\hat{D_k})_{ii} = max \{|D_k|_{i, i} ; \alpha \}$, $\forall i = \overline{1, d}$
    \State $\eta_k = min \{ \sqrt{1 + \theta_{k-1}} \cdot \eta_{k-1}; \frac{||w_k - w_{k-1}||_{\hat{D_k}}}{2 ||\nabla F(w_k) - \nabla F(w_{k-1}) ||_{\hat{D_k}}^* } \}$
    \State $\theta_k = \frac{\eta_k}{\eta_{k-1}}$
    \EndFor

\end{algorithmic}
\end{algorithm}

Now we will show the main differences between the methods of AdamL2, AdamW and MyAdamW -- the algorithm that we propose in this article

@@

\bibliographystyle{unsrtnat}
\bibliography{references}
\section{Appendix}

@@
